Commutative Character Sheaves

### 2015-11-18 followup.tex
New abstract

\begin{abstract}
We introduce and establish the basic properties of  the category of \emph{commutative character sheaves} on smooth group schemes $G$ over finite fields $\Fq$, building on earlier work by the same authors.
We use this category to geometrize types for supercuspidal representations of $p$-adic groups. 
\end{abstract}

>>>>

\begin{abstract}
We generalize the function-sheaf dictionary to arbitrary smooth group schemes over finite fields.  In previous work,
we considered the case of smooth commutative group schemes and found that the standard definition of
character sheaves produced a dictionary with a nontrivial kernel.  In this paper, we give a modification of
the category of character sheaves that remedies this defect, and is also extensible to non-commutative groups.
We use these \emph{commutative character sheaves} to geometrize types for supercuspidal representations of
$p$-adic groups. 
\end{abstract}
